


\begin{longtable} {|m{0.1\textwidth}|m{0.8\textwidth}|m{0.1\textwidth}|}
\hline
\textbf{ID} & \textbf{ITEM} & \textbf{CHECK} \\
\hline
\multicolumn{2}{|l|}{ \textbf{SCIENCE} } & \\
\hline
& \textbf{CAC} & \\
\hline
S1 & Remove the CAC wall with the D-SUB connector, if it's not removed already. & \\ \hline
S2 & Connect picarro to quick connector stem at No 10. & \\ \hline
S3 & Attach the fill gas bottle's quick connector stem to quick connector body No 1. & \\ \hline
S4 & Let the fill gas run through the AirCore at a flow rate of 40ml/min. & \\ \hline
S5 & Leave it flushing over night. & \\ \hline
S6 & Detach quick connector stem at No 1. & \\ \hline
S7 & Detach the quick connector stem at No 10. & \\ \hline
S8 & Disconnect the picarro analyser. & \\ \hline
S9 & Connect the dryer tube No 14 to No 13. & \\ \hline
S10 & Connect parts 11 to 21. & \\ \hline
S11 & Check all connections are tighten. & \\ \hline
S12 & Close the CAC's solenoid valve No 17. & \\ \hline
S13 & Connect quick connector stem No 10 to No 9. & \\ \hline
S14 & Connect No 10 with No 11. & \\ \hline
S15 & Check all connections are tighten. & \\ \hline
S16 & Put the CAC wall with the D-SUB connector back. & \\ \hline
& \textbf{AAC/MANIFOLD} & \\ \hline
S17 & Unscrew the plug from the inlet (1) and outlet tube (29). & \\ \hline
S18 & Screw in the male threaded quick connector to the inlet tube (1). & \\ \hline
S19 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S20 & Open flushing valve (27). & \\ \hline
S21 & Turn central valve on so that is open to dry gas. & \\ \hline
S22 & Let the dry gas run through the AAC's manifold for 10 minutes. & \\ \hline
S23 & Close flushing valve (27) & \\ \hline
S24 & Turn central valve off so that is close to dry gas. & \\ \hline
S25 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S26 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
& \textbf{AAC/TUBES/BAGS} & \\ \hline
S27 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S28 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S29 & Open 1st bag's manual valve. & \\ \hline
S30 & Open flushing valve (27). & \\ \hline
S31 & Open 1st bag's solenoid valve in the manifold (23) & \\ \hline
S32 & Open central valve so that is open to dry gas. & \\ \hline
S33 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S34 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S35 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S36 & Turn the central valve open to dry gas. & \\ \hline
S37 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S38 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S39 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S40 & Repeat steps S36 to S39 one more time. & \\ \hline
S41 & Close 1st bag's solenoid valve in the manifold (23). & \\ \hline
S42 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S43 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S44 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S45 & Turn central valve on so that is open to dry gas. & \\ \hline
S46 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S47 & Close flushing valve (27) & \\ \hline
S48 & Turn central valve off so that is close to dry gas. & \\ \hline
S49 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S50 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
S51 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S52 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S53 & Open 2nd bag's manual valve. & \\ \hline
S54 & Open flushing valve (27). & \\ \hline
S55 & Open 2nd bag's solenoid valve in the manifold (23) & \\ \hline
S56 & Open central valve so that is open to dry gas. & \\ \hline
S57 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S58 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S59 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S60 & Turn the central valve open to dry gas. & \\ \hline
S61 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S62 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S63 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S64 & Repeat steps S60 to S63 one more time. & \\ \hline
S65 & Close 2nd bag's solenoid valve in the manifold (23). & \\ \hline
S66 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S67 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S68 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S69 & Turn central valve on so that is open to dry gas. & \\ \hline
S70 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S71 & Close flushing valve (27) & \\ \hline
S72 & Turn central valve off so that is close to dry gas. & \\ \hline
S73 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S74 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
S75 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S76 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S77 & Open 3rd bag's manual valve. & \\ \hline
S78 & Open flushing valve (27). & \\ \hline
S79 & Open 3rd bag's solenoid valve in the manifold (23) & \\ \hline
S80 & Open central valve so that is open to dry gas. & \\ \hline
S81 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S82 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S83 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S84 & Turn the central valve open to dry gas. & \\ \hline
S85 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S86 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S87 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S88 & Repeat steps S84 to S87 one more time. & \\ \hline
S89 & Close 3rd bag's solenoid valve in the manifold (23). & \\ \hline
S90 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S91 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S92 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S93 & Turn central valve on so that is open to dry gas. & \\ \hline
S94 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S95 & Close flushing valve (27) & \\ \hline
S96 & Turn central valve off so that is close to dry gas. & \\ \hline
S97 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S98 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
S99 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S100 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S101 & Open 4th bag's manual valve. & \\ \hline
S102 & Open flushing valve (27). & \\ \hline
S103 & Open 4th bag's solenoid valve in the manifold (23) & \\ \hline
S104 & Open central valve so that is open to dry gas. & \\ \hline
S105 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S106 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S107 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S108 & Turn the central valve open to dry gas. & \\ \hline
S109 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S110 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S111 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S112 & Repeat steps S108 to S111 one more time. & \\ \hline
S113 & Close 4th bag's solenoid valve in the manifold (23). & \\ \hline
S114 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S115 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S116 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S117 & Turn central valve on so that is open to dry gas. & \\ \hline
S118 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S119 & Close flushing valve (27) & \\ \hline
S120 & Turn central valve off so that is close to dry gas. & \\ \hline
S121 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S122 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
S123 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S124 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S125 & Open 5th bag's manual valve. & \\ \hline
S126 & Open flushing valve (27). & \\ \hline
S127 & Open 5th bag's solenoid valve in the manifold (23) & \\ \hline
S128 & Open central valve so that is open to dry gas. & \\ \hline
S129 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S130 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S131 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S132 & Turn the central valve open to dry gas. & \\ \hline
S133 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S134 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S135 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S136 & Repeat steps S132 to S135 one more time. & \\ \hline
S137 & Close 5th bag's solenoid valve in the manifold (23). & \\ \hline
S138 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S139 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S140 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S141 & Turn central valve on so that is open to dry gas. & \\ \hline
S142 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S143 & Close flushing valve (27) & \\ \hline
S144 & Turn central valve off so that is close to dry gas. & \\ \hline
S145 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S146 & Screw in the plug to the AAC inlet tube (1). & \\ \hline
S147 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S148 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S149 & Open 6th bag's manual valve. & \\ \hline
S150 & Open flushing valve (27). & \\ \hline
S151 & Open 6th bag's solenoid valve in the manifold (23) & \\ \hline
S152 & Open central valve so that is open to dry gas. & \\ \hline
S153 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S154 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S155 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S156 & Turn the central valve open to dry gas. & \\ \hline
S157 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S158 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S159 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S160 & Repeat steps S156 to S159 one more time. & \\ \hline
S161 & Close 6th bag's solenoid valve in the manifold (23). & \\ \hline
S162 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S163 & Unscrew the plug from the AAC inlet tube (1). & \\ \hline
S164 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S165 & Turn central valve on so that is open to dry gas. & \\ \hline
S166 & Let the dry gas run through the AAC's manifold for 2 minutes. & \\ \hline
S167 & Close flushing valve (27) & \\ \hline
S168 & Turn central valve off so that is close to dry gas. & \\ \hline
S169 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S170 & Screw in the plug to the AAC inlet tube (1). & \\ \hline



\multicolumn{2}{|l|}{  \textbf{ELECTRICAL} } & \\ \hline
E1 & Check that all (3 9-Pin, Bags, Out, CAC, and 2 15-pin, Level 1 and 2) D-subs are connected and screwed in on the PCB (hand tight, DO NOT TIGHTEN TO HARD). & \\ \hline
E2 & Check that plastic 28.8V power is connected to level 1 and 2 connectors (Red wire, plastic connector, Male on wires going to each level, female is underneath the PCB.).& \\ \hline
E3 & Check that the plastic 28.8V power cable from the PCB is secured with zip tie to one of the standoffs. & \\ \hline 
E4 & Check that power is plugged in on the PCB. & \\ \hline
E5 & Check that Ethernet is connected form PCB to wall. (should hear click) & \\ \hline
E6 & Check that outside pressure sensors are connected to the outside upper (furthest from frame) 9-pin D-sub wall connector (hand tight, DO NOT TIGHTEN TO HARD). & \\ \hline
E7 & Check that CAC is connected on the outside lower (closest to frame) 9-pin D-sub wall connector (hand tight, DO NOT TIGHTEN TOO HARD). & \\ \hline
E8 & Check that power is connected on the outside wall. & \\ \hline
E9 & Check that the Ethernet is connected on the outside wall (should hear click). & \\ \hline
E10 & Check main PCB board is secure (Locking nuts where possible and no nut for the rest).\\ \hline
E11 & Check that pressure sensors are secure on the outside (Bolted down with locking nuts). & \\ \hline
E12 & Check output voltage from DCDC's and make sure they are used equally (after diode). & \\ \hline
E13 & Verify sensors give data to ground station. & \\ \hline
E14 & Verify that all valves open and close as expected (listen and check PCB lights).& \\ \hline
E15 & Verify that heaters get warm when they are turned on (Check temp data, feel, and check lights)& \\ \hline
\multicolumn{2}{|l|}{  \textbf{SOFTWARE} } & \\ \hline
SW1 & The ground station laptop PC will need to be put in place and operational. & \\ \hline
SW2 & The correct version of the onboard software have been uploaded to the OBC. & \\ \hline
SW3 & The communication through E-link with the experiment shall be tested. & \\ \hline
SW4 & Verify that the data from sensors are  realistic. & \\ \hline
SW5 & The air sampling itinerary is checked. & \\ \hline
SW6 & SD card contents are checked. & \\ \hline
\multicolumn{2}{|l|}{ \textbf{MECHANICAL} } & \\
\hline
M1 & Check that the frame structure is properly fixed. & \\
\hline
M2 & Check that the handles of both boxes are properly fixed. & \\
\hline
& \textbf{AAC BOX} & \\
\hline
M3 & Check that The Brain is properly attached to the structure of the AAC Box. & \\
\hline
M4 & Check that all the pneumatic connections are set (interfaces, valves, bags): use the manufactured tool for this matter. & \\
\hline
M5 & Check that the bags valve are open. & \\
\hline
M6 & Check that the bags are properly fixed with the circular bar. & \\
\hline
M7 & Check that the electronic interfaces panel is properly fixed to the top wall. & \\
\hline
M8 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
M9 & Unscrew the plugs from the inlet and the outlet tube. & \\
\hline
& \textbf{CAC BOX} & \\
\hline
M10 & Check that the AirCore is properly placed. & \\
\hline
M11 & Check that all the pneumatic connections are set (interfaces, valves) & \\
\hline
M12 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
M13 & Unscrew the plug from the inlet/outlet tube. & \\
\hline
& \textbf{GONDOLA} & \\
\hline
M14 &  Attach both boxes one to the other. & \\
\hline
M15 & Introduce both boxes inside the gondola. & \\
\hline
M16 & Check that the experiment box is fixed to the gondola rails (10 anchor points). & \\
\hline
M17 & Check that the electronic connectors are properly fixed to both electronic panels (D-sub, power, E-link) & \\
\hline


\end{longtable}
