


\begin{longtable} {|m{0.1\textwidth}|m{0.8\textwidth}|m{0.1\textwidth}|}
\hline
\textbf{ID} & \textbf{ITEM} & \textbf{CHECK} \\
\hline
\multicolumn{2}{|l|}{ \textbf{SCIENCE} } & \\
\hline
& \textbf{CAC} & \\
\hline
S1 & Connect picarro to quick connector stem at No 6. & \\
\hline
S2 & Attach quick connector stem to quick connector body No 1. & \\
\hline
S3 & Start flushing the CAC with a fill gas at a flow rate of 40ml/min, the night before the flight. & \\
\hline
S4 & Leave it flushing over night. & \\
\hline
S5 & Detach the quick connector stem at No 1. & \\
\hline
S6 & Detach the quick connector stem at No 6. & \\
\hline
S6 & Disconnect the picarro analyser. & \\
\hline
S7 & Fill the dryer tube with magnesium perchlorate powder (~2gr), YY hr before flight. DO NOT PACK IT TOO DENSE. IT HAS TO BE LOOSELY PACKED. & \\
\hline
S8 & Connect the dryer tube (No 7.) to No 6. & \\
\hline
S9 & Connect parts 7 to 13. & \\
\hline
S10 & Close solenoid valve no 10. & \\
\hline
S11 & Connect quick connector stem No 6. to No 5. & \\
\hline
S12 & Place the CAC in its box. & \\
\hline
& \textbf{AAC BAGS} & \\
\hline
S15 & Connect the vacuum pump, the dry gas bottle, and one bag with a central valve. & \\
\hline
S16 & Connect a flow rate sensor close to the central valve. (valve that controls vacuum or filling bags). & \\
\hline
S17 & Open bag's manual valve. & \\
\hline
S18 & Turn the central valve in the position where the vacuum pump is closed but the dry gas can go through. & \\
\hline
S19 & Start filling the bag with 3 L of dry gas with a flow rate lower than 3 L/min (we can start with 1.5 L/min). & \\
\hline
S20 & As soon as the bag is full, turn the central valve in the position where the vacuum pump is open (active) and the dry gas is blocked, allowing the bag to empty. & \\
\hline
S21 & Turn the central valve in the position where the vacuum pump is closed but the dry gas can go through. & \\
\hline
S22 & Increase the flow rate to 3 L/min. & \\
\hline
S23 & As soon as the bag is full, turn the central valve in the position where the vacuum pump is open (active) and the dry gas is blocked, allowing the bag to empty. & \\
\hline
S24 & Again, turn the central valve in the position where the vacuum pump is closed but the dry gas can go through. & \\
\hline
S25 & As soon as the bag is full again, turn the central valve in the position where the vacuum pump is open (active) and the dry gas is blocked, allowing the bag to empty. & \\
\hline
S26 & Repeat one more time. Total 3 times. & \\
\hline
S27 & Close bag's manual valve. & \\
\hline
S28 & Remove bag. & \\
\hline
S29 & Connect the second bag. & \\
\hline
S30 & Repeat the filling-emptying procedure 3 times, as before. & \\
\hline
S31 & Repeat for all bags. & \\
\hline
S32 & At the end of this process, all the bags have to be placed inside the AAC box connecting them to the respective T-Union interface by means of a nut ferrule & \\
\hline
S33 & The manual valves of the bags shall be opened before the flight & \\
\hline
& \textbf{AAC TUBES} & \\
\hline
S34 & Open flushing valve (23). & \\
\hline
S35 & Open the 1st tube valve (28) that is connected to the first bag (31). & \\
\hline
S36 & Open the respective solenoid valve (26) in manifold (19). & \\
\hline
S37 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S38 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S39 & Disconnect dry gas bottle. & \\
\hline
S40 & Close tube valve 1 (28). & \\
\hline
S41 & Close solenoid valve (26) in manifold (19). & \\
\hline
S42 & Open the 2nd tube valve (28). & \\
\hline
S43 & Open the respective solenoid valve (26) in manifold (19). & \\
\hline
S44 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S45 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S46 & Disconnect dry gas bottle. & \\
\hline
S47 & Close the 2nd tube valve (28). & \\
\hline
S48 & Close the solenoid valve 2 (26) in manifold (19). & \\
\hline
S49 & Open tube valve 3 (28). & \\
\hline
S50 & Open solenoid valve 3 (26) in manifold (19). & \\
\hline
S51 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S52 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S53 & Disconnect dry gas bottle. & \\
\hline
S54 & Close tube valve 3 (28). & \\
\hline
S55 & Close solenoid valve 3 (26) in manifold (19). & \\
\hline
S56 & Open tube valve 4 (28). & \\
\hline
S57 & Open solenoid valve 4 (26) in manifold (19). & \\
\hline
S58 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S59 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S60 & Disconnect dry gas bottle. & \\
\hline
S61 & Close tube valve 4 (28). & \\
\hline
S62 & Close solenoid valve 4 (26) in manifold (19). & \\
\hline
S63 & Open tube valve 5 (28). & \\
\hline
S64 & Open solenoid valve 5 (26) in manifold (19). & \\
\hline
S65 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S66 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S67 & Disconnect dry gas bottle. & \\
\hline
S68 & Close tube valve 5 (28). & \\
\hline
S69 & Close solenoid valve 5 (26) in manifold (19). & \\
\hline
S70 & Open tube valve 6 (28). & \\
\hline
S71 & Open solenoid valve 6 (28) in manifold (19). & \\
\hline
S72 & Connect dry gas bottle at tube valve T-union (29). & \\
\hline
S73 & Start flushing. Amount: 10 times the tube's volume for as long as it's necessary (and a little bit longer). & \\
\hline
S74 & Disconnect dry gas bottle. & \\
\hline
S75 & Close tube valve 6 (28). & \\
\hline
S76 & Close solenoid valve 6 (26) in manifold (19). & \\
\hline
S77 & Start pump (7) to flush the system for YY time. & \\
\hline
S78 & Stop the pump. & \\
\hline
S79 & Close flushing valve (23). & \\
\hline
S80 & All the valves must be closed. & \\
\hline
S81 & Fill the dryer tube (3) with 25 gr of magnesium perchlorate. (DO NOT PACK TOO DENSE. IT HAS TO BE LOOSELY PACKED). & \\
\hline
S82 & Connect the dryer as shown in the schematic. & \\
\hline
\multicolumn{2}{|l|}{ \textbf{ELECTRICAL} } & \\
\hline
E1 & Verify all electrical components are working: & \\
\hline
E2 & Sensors & \\
\hline
E3 & Valves & \\
\hline
E4 & Pump & \\
\hline
E5 & Heaters & \\
\hline
E6 & Check all connections and fix any loose connections (particularly the connection between the boxes.) & \\
\hline
E7 & Check LED display is showing all parts are alive & \\
\hline
E8 & Check connection with the gondola (e-link and power) & \\
\hline
E9 & Check all pcb boards and sensors are secure & \\
\hline
E10 & Verify again that components are working and check LED display is still showing all parts are alive & \\
\hline
\multicolumn{2}{|l|}{ \textbf{SOFTWARE} } & \\
\hline
SW1 & The ground station laptop PC will need to be put in place and operational. & \\
\hline
SW2 & The correct version of the onboard software have been uploaded to the OBC. & \\
\hline
SW3 & The communication through E-link with the experiment shall be tested. & \\
\hline
SW4 & The air sampling itinerary is checked. & \\
\hline
\multicolumn{2}{|l|}{ \textbf{MECHANICAL} } & \\
\hline
M1 & Check that the frame structure is properly fixed. & \\
\hline
M2 & Check that the handles of both boxes are properly fixed. & \\
\hline
& \textbf{AAC BOX} & \\
\hline
M3 & Check that The Brain is properly attached to the structure of the AAC Box. & \\
\hline
M4 & Check that all the pneumatic connections are set (interfaces, valves, bags): use the manufactured tool for this matter. & \\
\hline
M5 & Check that the bags are properly fixed with the circular bar. & \\
\hline
M6 & Check that the electronic interfaces panel is properly fixed to the top wall. & \\
\hline
M7 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
& \textbf{CAC BOX} & \\
\hline
M8 & Check that the AirCore is properly placed. & \\
\hline
M9 & Check that all the pneumatic connections are set (interfaces, valves) & \\
\hline
M10 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
& \textbf{GONDOLA} & \\
\hline
M11 &  Attach both boxes one to the other. & \\
\hline
M12 & Introduce both boxes inside the gondola. & \\
\hline
M13 & Check that the experiment box is fixed to the gondola rails (10 anchor points). & \\
\hline
M14 & Check that the electronic connectors are properly fixed to both electronic panels (D-sub, power, E-link) & \\
\hline

\end{longtable}
