\begin{longtable}{|m{0.09\textwidth}| m{0.51\textwidth} |m{0.03\textwidth} |m{0.03\textwidth}|m{0.11\textwidth}| m{0.65\textwidth}|}

\hline
\textbf{ID} & \textbf{Risk (\& consequence if)} & \textbf{P} & \textbf{S} & \textbf{P * S} & \textbf{Action} \\ \hline
TC10 & Software fails to store data & B & 4 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: Extensive testing will be done \\ \hline
TC20 & Failure of several sensors & B & 3 & \cellcolor[HTML]{FCFF2F}Low & Thermal test to approve the functionality of the experiment. \\ \hline
TC30 & Critical component is destroyed in testing & B & 1 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: Spare components can be ordered. \\ \hline
TC40 & Electrical connections dislodges or short circuits because of vibration or shock & B & 3 & \cellcolor[HTML]{FCFF2F}Low & Unacceptable risk. Careful soldering and extensive testing will be applied. \\ \hline
TC50 & Experiment electronics fail due to long exposure to cold or warm temperatures & B & 2 & \cellcolor[HTML]{34FF34}Very Low & Unacceptable Risk: Thermomechanical and thermoelectrical solutions will be simulated and tested in detail to help prevent this from happening. \\ \hline
TC60 & Software and electrical fail to control heaters causing temperature to drop or rise below or above operational range & B & 2 & \cellcolor[HTML]{34FF34}Very Low & Unacceptable risk: Tests will be performed prior to the flight to detect and minimize the risk of occurrence.The system will be monitored during flight and handled manually if necessary. \\ \hline
TC70 & Software fails to enter safe mode (may result in loss of data) & B & 3 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: Extensive testing will be done. \\ \hline
TC80 & On-board memory will be full (flight time longer than expected) & A & 2 & \cellcolor[HTML]{34FF34}Very Low & Acceptable Risk: The experiment shall go through extensive testing to determine the required memory size and make sure that data is not overwritten if memory is full. \\ \hline
TC90 & Connection loss with ground station & A & 4 & \cellcolor[HTML]{34FF34}Very Low & Acceptable Risk: Experiment will be designed to operate autonomously. \\ \hline
TC100 & Software fails to control valves autonomously & B & 4 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: Extensive testing will be done. Telecommand will also be used to manually control the valves. \\ \hline
TC110 & Software fails to change modes autonomously & B & 4 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: Extensive testing will be done. Telecommand will also be used to manually change experiment modes. \\ \hline
TC120 & Complete software failure & B & 4 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: Watchdog timer will be applied to reset software if it freezes. \\ \hline
TC130 & Failure of fast opening system & B & 2 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: the box could also be opened but a little bit slower. \\ \hline
TC140 & The gas analyzer isn't properly calibrated and returns inaccurate results & B & 4 & \cellcolor[HTML]{FCFF2F}Low & Acceptable risk: Calibrate the gas analyzer before use.\\ \hline
MS10 & Down link connection is lost & B & 2 & \cellcolor[HTML]{34FF34}Very Low & Acceptable Risk: Data will also be saved on SD card. \\ \hline
MS20 & Condensation on experiment PCBs which could causes short circuits & A & 3 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: \hl{Circuit box will be sealed to prevent condensation.} \st{Spare components can be ordered.} \\ \hline
MS30 & Temperature sensitive components that are essential to full the mission objective might be below their operating temperature. & C & 3 & \cellcolor[HTML]{FCFF2F}Low & Safe mode to prevent the components to operate out of its operating temperature range. \\ \hline
MS40 & Experiment lands in water causing electronics failure & B & 1 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: Check if SD card needs waterproof shell or is waterproof in itself. Also, all the necessary data will be downloaded during the flight. \\ \hline
MS50 & Interference from other experiments and/or balloon & A & 4 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: no action. \\ \hline
MS60 & Balloon power failure & C & 1 & \cellcolor[HTML]{34FF34}Very Low & Acceptable risk: \hl{Valves default state is closed so if all power is lost valves will automatically close preserving all samples collected up until that point.} \st{no action.} . \\ \hline
MS70 & Bags disconnect & C & 3 & \cellcolor[HTML]{FCFF2F}Low & The affected bags could not collect samples. A proper fixing of the flanges must be double checked.
\\ \hline
MS80 & Bags puncture & B & 3 & \cellcolor[HTML]{FCFF2F}Low & The affected bags could not collect samples. Proper protection will be placed in order to avoid puncture from external elements. \\ \hline
MS90 & Pump failure & B & 3 & \cellcolor[HTML]{FCFF2F}Low & The bags could not be filled and thus the AAC system would fail. It will be properly chosen and tested before the flight. \\ \hline
MS100 & Intake pipe blocked by external element & C & 3 & \cellcolor[HTML]{FCFF2F}Low & The bags could not be filled and thus the AAC system would fail. An air filter will be placed in both intake and outlet of the pipe to prevent it. \\ \hline
VE10 & SD-card is destroyed at impact & B & 3 & \cellcolor[HTML]{FCFF2F}Low & Acceptable Risk: All data will be transmitted to the ground. \\ \hline
VE20 & Gondola Fixing Interface & B & 4 & \cellcolor[HTML]{FCFF2F}Low & The experiment box could detach from the gondola’s rails. Proper fixing has been designed to prevent it. \\ \hline
VE30 & Structure damage due to bad landing & B & 3 & \cellcolor[HTML]{FCFF2F}Low & Landing directly on a hard element could break the structure or the protective walls. Consistent design implemented to prevent it. \\ \hline
VE40 & Hard landing damages the CAC equipment & C & 3 & \cellcolor[HTML]{FCFF2F}Low & Acceptable risk:  Proper  protection will be placed in order to avoid damage from hard landing \hl{and the experiment shall be mounted at the top of the gondola.} \\ \hline
VE50 & Hard landing damages the AAC equipment & C & 3 & \cellcolor[HTML]{FCFF2F}Low & Acceptable risk:  Proper  protection will be placed in order to avoid puncture from hard landing. \\ \hline
% & & & & &\\ \hline

%\end{tabular}
\caption{Risk Register}
\label{tab:risk-register}
\end{longtable}
\raggedbottom