\subsection{Timeline for Countdown and Flight}
Table \ref{tab:countflight} was the estimated timeline during countdown and flight. 

The desired altitudes in which air samples were to be collected with the sampling bags was associated with specific air pressure values. Thus, the valve operations to sample air during the balloon Ascent and Descent Phases were to be triggered by readings from the ambient pressure sensor. The time values presented in Table \ref{tab:countflight} merely served as an indicative estimate of when the sampling will take place as sampling was not programmed based on flight time.

\input{6-launch-campaign-preparation/tables/countdown-flight-timeline.tex}

Table \ref{tab:LaunchTimelineActuall} shows the actual timeline which occurred during flight. The in-flight pump startup failure that occurred is shown together with the relevant actions taken during the in flight analysis of what the problem might have been. The procedure of differential pressure difference is also shown. After attempting to start the pump several times the team recognised already that a likely cause of failure was related to the pump getting enough current, therefore several different procedures were attempted to start the pump. The first was attempting to turn the pump on when everything other than the Arduino was switched off. The second was heating the pump up until the temperature readings showed that the pump was near the top of its operating range and then attempting to turn it on, still with all other components except the Arduino turned off. Neither of these attempts worked. A third idea was to try and start it by creating a pressure difference during the descent, however this was not attempted as it risked the CAC sample. Instead during descent the valves were opened to attempt passive sampling of the bags. However due to the lack of pressure difference between the bag and the ambient pressure this had a low probability of success. 

\input{6-launch-campaign-preparation/tables/flight-actual-timeline.tex}