\subsection{Post Flight Activities}

\subsubsection{CAC Recovery}
It was important that the CAC was recovered as quickly as possible. The experiment had been designed so that the recovery team could easily remove the AirCore in the CAC box from the gondola without having to remove the entire experiment. This was to facilitate possible transportation back to Esrange via helicopter.

This quick recovery was important to minimize the length of time in which mixing of the gas occured in the collected CAC sample. The sample should be analyzed within five to six hours after the experiment lands. At PDR it was discussed that the CAC box could be brought back to Esrange on the helicopter instead of the truck. This situation was preferable for TUBULAR Team. 

The FMI team arrived at Esrange on the 12th of October with all the necessary equipment for pre-flight flushing and post-flight analysis. Having the FMI team at Esrange gave additional time for them to install and calibrate their lab equipment and also allowed them to proceed faster with the analysis process as soon as the CAC was returned to Esrange. 

Detailed instructions were provided on how to remove the CAC box. In addition, instructions were provided to ensure that the system was completely shut down and the valves secured. Shutdown was automated, however, a manual shutdown mechanism was included should the automation fail.

\subsubsection{Recovery Checklist}
\label{sec:recovery-checklist}

FAST RECOVERY OF CAC

\begin{itemize}
    \item Check no damage exists to outer structure and no white paste seen in inlet tubes, this confirms no leak and chemicals are SAFE.
    \item Screw on the three metal plugs provided to the inlet and outlet tubes.
    \item Unplug the gondola power cord from the AAC box. Circled with RED paint.
    \item Unplug the E-Link connection from the AAC box. Circled with RED paint.
    \item Unplug the D-Sub connector from the CAC Box. Circled with RED paint.
    \item Unscrew 6 screws in the outside face of the experiment. Painted in RED.
    \item Unscrew 6 screws in the inside face of the experiment. Painted in RED.
    \item Unscrew 2 gondola attachment points from the CAC
    \item Remove the CAC Box from the gondola. Handles located at the top of the box. 
\end{itemize}

The regular recovery of the AAC and the non nominal recovery of the experiment is listed in Section \ref{ssec:RecoveryCheck} of Appendix \ref{sec:Checklist}.

%The analysis results that will then be used for the post flight meeting. Further analysis will then be carried out to fully understand the data. Once a full analysis of the data has been completed there is the potential for publication of research findings.


\subsubsection{Analysis Preparation}

In order to efficiently remove ambient air moisture from the analyzer, a calibration gas had to run through the Picarro analyzer, after the gondola cut-off phase until the CAC analysis. The reason this was done was because it was necessary that the readings of the calibrating gas stabilized before starting the analysis and the presence of moisture would have made this stabilization slower. Having the analyzer running for a few hours before the CAC recovery, saved precious time as it made it possible to start the analysis as soon as the CAC was recovered. 



% After completing the flushing of the CAC, the picarro analyzer has to keep working. For that reason a calibrating gas will be connected to the analyzer and run through it, until the analysis of the CAC, preventing ambient air moisture to enter into the analyzer.
% It is necessary that the readings of the calibating gas running through the picarro analyzer have been stabilized before analyzing the CAC sample. This will distinguish where the collected air sample starts and where it stops. 
% So, having the analyzer running during the flight will save precious time, and    Using a gas with known concentrations will make easy the distinguish between the collected samples and    By the time the CAC is recovered, the readings of the picarro will have stabilize and the analysis will start immediately.   


