\section*{Acknowledgements} \markboth{}{}

The TUBULAR Team wishes to acknowledge the invaluable support received by the REXUS/BEXUS organizers, SNSB, DLR, ESA, SSC, ZARM, Esrange Space Centre, and ESA Education. In particular, the team's gratitude extends to the following project advisers who show special interest in our experiment:

\begin{itemize}
  \item \textbf{Dr. Rigel Kivi}, Senior Scientist at the Finnish Meteorological Institute (FMI). A key project partner, Dr. Kivi's research and experience in Arctic atmospheric studies serves as a knowledge-base reference that ensures proper design of the experiment.
  \item \textbf{Mr. Pauli Heikkinen}, Scientist at FMI. A key project partner, Dr. Heikkinen's research and experience in Arctic atmospheric studies serves as a knowledge-base reference that ensures proper design of the experiment.
  \item \textbf{Dr. Uwe Raffalski}, Associate Professor at the Swedish Institute of Space physics (IRF) and the project's endorsing professor. Dr. Raffalski's research and experience in Arctic atmospheric studies serves as a knowledge-base reference that ensures proper design of the experiment.
  \item \textbf{Dr. Thomas Kuhn}, Associate Professor at Luleå  University of Technology (LTU). A project course offered by Dr. Kuhn serves as a merited university module all while providing the team with guidance and supervision.
  \item \textbf{Mr. Olle Persson}, Operations Administrator at Luleå University of Technology (LTU). A former REXUS/BEXUS affiliate, Mr. Persson has been providing guidance based on his experience.
  \item \textbf{Mr. Grzegorz Izworski}, Electromechanical Instrumentation Engineer at European Space Agency (ESA). Mr. Izworski is the team's mentor supporting design and development of the project to ensure launch success.
  \item \textbf{Mr. Koen Debeule}, Electronic Design Engineer at European Space Agency (ESA). Mr. Debeule is the team's supporting mentor.
  \item \textbf{Mr. Vince Still}, LTU alumni and previous BEXUS participant with project EXIST. Mr Still assists the team as a thermal consultant.
\end{itemize}

The TUBULAR Team would also like to acknowledge component sponsorship from the following manufacturers and suppliers all of which showed authentic interest in the project and provided outstanding support:

\begin{itemize}
  \item \textbf{Restek} develops and manufactures GC and LC columns, reference standards, sample prep materials, and accessories for the international chromatography industry. 
  \item \textbf{SMC Pneumatics} specializes in pneumatic control engineering to support industrial automation. SMC develops a broad range of control systems and equipment, such as directional control valves, actuators, and air line equipment, to support diverse applications.
  \item \textbf{Teknolab Sorbent} provides products such as  analysis instruments and accessories within reference materials, chromatography and separation technology.
  %\item \textbf{Parker} develops and manufactures motion and control technologies. Precision engineered solutions for Aerospace, Climate Control, Electromechanical, and Filtration.
  \item \textbf{Lagers Masking Consulting} specializes in maintenance products and services for industry, construction, and municipal facilities.
  \item \textbf{Bosch Rexroth} manufactures products and systems associated with the control and motion of industrial and mobile equipment.
\end{itemize}