\subsection{Functional Requirements}

\begin{enumerate}
    \item[F.1] \st{The experiment \textit{shall} collect air samples.}\footnote{Unnecessary requirement that has been removed.\label{fn:unnecessary-requirement}}
    \item[F.2] The experiment \textit{shall} collect air samples by the CAC.
    \item[F.3] The experiment \textit{shall} collect air samples by the AAC.
    \item[F.4] \st{The experiment's AAC System \textit{shall} be able to collect air samples during the ascent phase.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.5] \st{The experiment's AAC System \textit{shall} be able to collect air samples during the descent phase.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.6] The altitude from which a sampling bag will start sampling \textit{shall} be programmable.
    \item[F.7] The altitude from which a sampling bag will stop sampling \textit{shall} be programmable.
    \item[F.8] \st{The experiment \textit{shall} pump air into the AAC Sampling Bags.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.9] The experiment \textit{should} collect data on the air intake flow to the AAC.
    \item[F.10] The experiment \textit{shall} collect data on the air pressure.
    \item[F.11] The experiment \textit{shall} collect data on the temperature.
    \item[F.12] The experiment \textit{shall} collect data on the humidity.
    \item[F.13] \st{The experiment \textit{shall} measure the temperature inside the AAC Valve Box.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.14] \st{The experiment \textit{should} measure the humidity inside the AAC Valve Box.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.15] \st{The experiment \textit{shall} collect data on the time.}\footnote{Unverifiable requirement that has been removed.\label{fn:unverifiable-requirement}}
    \item[F.16] \st{The experiment \textit{shall} accept telecommand instructions to program AAC sampling altitudes for each sampling bag.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.17] \st{The experiment \textit{shall} accept telecommand instructions to open designated valves.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.18] \st{The experiment \textit{shall} accept telecommand instructions to close designated valves.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.19] \st{The experiment \textit{may} accept telecommand instructions to change the sampling rate of the ambient pressure sensor.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.20] \st{The experiment \textit{may} accept telecommand instructions to change the sampling rate of the ambient temperature sensor.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.21] \st{The experiment \textit{may} accept telecommand instructions to change the sampling rate of the AAC Valve Box temperature sensor.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.22] \st{The experiment \textit{may} accept telecommand instructions to turn on the air pump.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.23] \st{The experiment \textit{may} accept telecommand instructions to turn off the air pump.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.24] \st{The experiment \textit{may} accept telecommand instructions to turn on the Valve Heater.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.25] \st{The experiment \textit{may} accept telecommand instructions to turn off the Valve Heater.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.26] \st{The experiment \textit{may} accept telecommand instructions to turn on the Electronics Box Heater.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item[F.27] \st{The experiment \textit{may} accept telecommand instructions to turn off the Electronics Box Heater.}\textsuperscript{\ref{fn:unnecessary-requirement}}
\end{enumerate}