\subsection{Design Requirements}

\begin{enumerate}[label=D.\arabic*]
    \item The experiment \textit{shall} operate in the temperature profile of the BEXUS flight.
    \item The experiment \textit{shall} operate in the vibration profile of the BEXUS flight.
    \item \st{The experiment \textit{shall} not disturb or harm the launch vehicle.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item The experiment's communication system \textit{shall} be compatible with the gondola's E-link system.
    \item The experiment's power supply \textit{shall} be compatible with the gondola's provided power.
    \item \st{The experiment \textit{shall} not disturb other experiments on the gondola.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item The total DC current draw \textit{should} be below 1.8 A.
    \item The total power consumption \textit{should} be below 374 Wh.
    \item \st{The experiment \textit{shall} be able to operate in low pressure conditions (10-15 mbar) up to 30 km altitude.}\footnote{Repeated in D18\label{fn:repeat-d18}}
    \item \st{The components of the experiment \textit{shall} operate within their temperature ranges.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item \st{The OBC \textit{shall} be able to autonomously control the heaters.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item \st{The ground station GC \textit{shall} be able to display some of the received data.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item \st{The experiment \textit{shall} be able to survive and operate between -30\degree C and 60\degree C.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item \st{The external components that are directly exposed to the outside environment \textit{shall} be able to operate at -70\degree C.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item \st{The watchdog \textit{should} be able to reset the system.}\textsuperscript{\ref{fn:unnecessary-requirement}}
    \item The experiment \textit{shall} be able to autonomously turn itself off just before landing.
    \item The experiment box \textit{shall} be placed with at least one face exposed to the outside.
    \item The experiment \textit{shall} operate in the pressure profile of the BEXUS flight.
    \item The experiment \textit{shall} operate in the vertical and horizontal accelerations profile of the BEXUS flight.
    \item \st{The experiment \textit{shall} operate in the
    horizontal accelerations profile of the BEXUS flight.}\footnote{Combined with D19\label{fn:combi-d19}}
    \item The experiment \textit{shall} be attached to the gondola's rails.
    \item The telecommand data rate \textit{shall} not be over 10kb/s.
    \item The air intake rate of the air pump \textit{shall} be minimum 3L/min at 24km altitude.
    \item The temperature of the Electronics Box \textit{shall} be between 0$\degree$C and 25$\degree$C.
    \item The temperature of the AAC Valve Box \textit{shall} be between 0$\degree$C and 25$\degree$C.
    \item The air sampling systems \textit{shall} filter out all water molecules before filling the sampling bags.
    \item The total weight of the experiment \textit{shall} be less than $28 kg$.
    \item The AAC box \textit{shall} be able to fit at least $6$ air sampling bags.
    \item The CAC box \textit{shall} take less than 3 minutes to be removed from the gondola without removing the whole experiment.
    \item The AAC \textit{shall} be re-usable for future balloon flights.
\end{enumerate}