\begin{longtable}{|m{0.12\textwidth}|m{0.4\textwidth}|m{0.4\textwidth}|}
\hline
\textbf{Risk} & \textbf{Key Characteristics} & \textbf{Mitigation}                                                           \\ \hline
\st{Flammable substances}    & \st{Styrofoam Brand Foam is oil based and is highly flammable}\footnote{Styrofoam has been found to only pose a flammable hazard when heated to at least 346$\degree{C}$.\cite{dowsverige}\label{fn:keychar}} & \st{Extensive testing will be performed to make sure there is no heat/fire source} \\ \hline
Sharp or cutting edges & Edges along the experiment                                & File down edges and cover them with tape                                                              \\ \hline
Chemical substances & Chemicals could be exposed after a hard landing & Magnesium Perchlorate filter mechanism is sealed and has been used before without any problem. In case of exposure after a hard impact, use protective goggles and gloves to avoid contact with the eyes and skin. The small quantities used for the experiment will not be a threat for the environment. Magnesium Perchlorate alone is not flammable but may cause or intensify fire in case of contact with combustible material. Therefore, the filter is made of stainless steel, which has high durability.       \\ \hline

Pressure Vessels & Compressed fluid containers can pose a risk of exploding if damaged & Pressurised gas will be used to flush the system before flight and to calibrate the sensors before analysing our samples after landing. NO pressurised vessels will fly. 
Three gas cylinders will be brought to Esrange by FMI. The cylinders will contain compressed dry air: \newline
Flush gas for the bag sampler: 20L at 140 bar \newline
Calibration gas for Picarro: 14L at 130 bar \newline
Flush/fill gas for AirCore: 26.8L at 110 bar (there will be 13 ppm CO in the cylinder) \\ \hline

\caption{Experiment Safety Risks.}
\label{tab:safrisk}
\end{longtable}
\raggedbottom